Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 abstract.tex
minor tweak of abstract.

The computing systems used by LHC experiments has historically consisted of
the federation of hundreds to thousands of distributed resources, ranging in
scale from small to mid-size resource.  In spite of the impressive scale of
the existing distributed computing solutions, the federation of small to mid-
size resources will be insufficient to meet projected demands of Run 3 (and
4). This paper is a case study of how the ATLAS experiment has embraced Titan
-- a DOE leadership facility in conjunction with traditional distributed high-
throughput computing to reach sustained production scales of approximately 51M
core-hours a years. The three main contributions of this paper are:  (i) a
critical evaluation of design and operational considerations  to support the
sustained, scalable and production usage of Titan;  (ii) a preliminary
characterization of a next generation executor for PanDA to support new
workloads and  advanced execution modes; and (iii) early lessons as  for how
current and future experimental and observational systems can be integrated
with production supercomputers and other platforms in a general and extensible
manner.

>>>>

The computing systems used by LHC experiments has historically consisted of
the federation of hundreds to thousands of distributed resources, ranging from
small to mid-size resource.  In spite of the impressive scale of the existing
distributed computing solutions, the federation of small to mid-size
resources will be insufficient to meet projected future demands.
This paper is a case study of how the ATLAS experiment has embraced Titan -- a
DOE leadership facility in conjunction with traditional distributed high-
throughput computing to reach sustained production scales of approximately 51M
core-hours a years. The three main contributions of this paper are:  (i) a
critical evaluation of design and operational considerations  to support the
sustained, scalable and production usage of Titan;  (ii) a preliminary
characterization of a next generation executor for PanDA to support new
workloads and  advanced execution modes; and (iii) early lessons for how
current and future experimental and observational systems can be integrated
with production supercomputers and other platforms in a general and extensible
manner.
